---
title: "Min-maxing with Me"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{minmaxme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## normalizeme()

This package is meant to help with the normalization of data frame (df) columns in a min-max type normalization. By design the most important functions are minmax() and organizeme(). While minmax() is a very basic min-max scaling calculation the second important function organizeme() helps with the wrangling of the minmax() output back into a neat and tidy df. 

Lets try both of them out:

```{r setup, message=FALSE, warning=FALSE, echo=TRUE}
# Load in this package 
library(normalizeme)

# And a shortcut for the other packages this function needs
library(tidyr)
library(dplyr)
library(readr)
library(stringr)
library(purrr)
library(forcats)
library(ggplot2)

# After loading in the package we normalize the raw data column using minmax
  output <- minmax(x = dataisme$raw_values)
# Then we run the output through organizeme() to get a df back
  organized_output <- organizeme(data = dataisme, minmax_output = output) 
# See the output from the functions:
  organized_output
```

As you can see we get the three columns we want. Good luck using this package!
